%% METHOD SECTION %%

\section{Method}

%This section describes the research methodologies used for data collection and data analysis. Additionally, it presents the characteristics of the papers in our reviewed corpus.

\subsection{Data Collection}
To perform a literature analysis of past findings on the relationship between the specifics of conversation architecture and perceptions of CAs, we identified, reviewed, and selected relevant literature using PRISMA guidelines \cite{prisma}. %, we reviewed and selected literature exploring the relationship between the specifics of conversation architecture elements and perceptions of CAs. 
In accordance with accepted practices, we defined the scope of our literature review by considering two factors: (1) time---specifically publications from 2010 to 2022---and (2) source---using the ACM Digital Library \mbox{\cite{zheng2022ux, stigall2019older, mcconvey2023human}.}
%Searches were carried out between January 1 and January 15, 2023. 
Through our analysis, we didn't find any common terms used to refer to either conversation architecture elements or aspects of perceptions. As such, we generalized our search term to capture articles related to conversational agents. Based on search terms used in previously published literature reviews \cite{clark2019state, rapp2021human}, the following keywords are used to search for publications related to conversational user interfaces:
\newline

\textit{"conversational agent" OR "natural language interface" OR "IPA" OR "intelligent personal assistant" OR "chatbot" OR "speech interface" OR "voice assistant" OR "intelligent agent" OR "human-chatbot communication" OR "virtual agent" OR "dialog* system" OR "voice user interface" OR "human computer dialog*"}
\newline

The following selection criteria are applied to identify literature related to the effect of conversational architecture on the perception of agents:
\begin{itemize}
  \item The paper was published between 2010 and 2022.
  \item The paper is peer-reviewed and written in English.
  \item The paper contains the use of voice-based or text-based conversational agents.
  \item The paper contains studies on the effect of conversation architecture elements on the perceptions of agents.
  \item The paper contains effects of conversation architecture elements can be separated from other effects (e.g. embodiment).

\end{itemize}

The initial query retrieved 2901 unique publications. We screened the titles and abstracts of the papers based on the selection criteria above, resulting in 221 papers. The fully body of these papers were then reviewed, selecting 49 papers that met the criteria. A search for additional literature based on citation tracing was also performed to supplement the corpus, adding 8 more papers to the selection. In total, we identified 57 relevant articles for analysis (see \autoref{fig:prisma}).

\input{figures/fig-prisma}

\subsubsection*{Literature Corpus Characteristics}

The papers reviewed (n=57) were published between May 2011 and November 2022. Most of the papers were published in or after 2019, with a slight trend upwards over the years (see \autoref{fig:paper}). The vast majority of the papers in our corpus were published in conference proceedings (n=50), while the remaining papers were published in journals. Out of the papers published in conferences, the top conferences were The ACM Conference on Human Factors in Computing Systems\footnote{https://dl.acm.org/conference/chi} (n=16), Conversational User Interfaces\footnote{https://dl.acm.org/conference/cui} (n=7), Human-Agent Interaction\footnote{https://dl.acm.org/conference/hai} (n=4), and Intelligent Virtual Agents\footnote{https://dl.acm.org/conference/iva} (n=4). 
%Out of the papers published in journals, some venues include the International Journal of Human-Computer Interaction\footnote{https://www.tandfonline.com/journals/hihc20} (n=2) and Interacting with Computers\footnote{https://academic.oup.com/iwc} (n=1).

On the modality characteristics of the conversational agents in our corpus, there is a roughly even split between voice and text modalities, with slightly more papers exploring voice-based CAs (n=30) compared to text-based CAs (n=27).

\input{figures/fig-paper}

\subsection{Data Analysis}

We analyzed the data by conducting reflexive thematic analysis approach with open and axial coding procedures \mbox{\cite{braun2019reflecting}}. First, we performed open coding on each article to extract labels related to perceptions of agents and conversation architecture. These labels were then grouped into conceptual categories through axial coding. The first author was responsible for performing the data analysis, with the second and third authors cross-checking the codes. We resolved disagreements through regular discussions and multiple rounds of revisions.

\subsubsection*{Perceptions of Agents} To understand the perceptions of agents related to conversation architecture (RQ1), assessments for the perceptions of agents were extracted from each paper. 
%We used inductive thematic analysis to group these assessments into codes based on their meanings. 
For example, likeability of the agent contains Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed}'s set of questions on likeability used by \cite{linnemann2018can}\cmt{[15]}, Subjective Assessment of Speech System Interface (SASSI) questionnaire \cite{hone2000towards}\cmt{sassi}'s set of questions on likeability used by \cite{chan2021kinvoices, choi2020nobody}\cmt{[74][54]} and questionnaire items like ``\textit{this voice agent was likeable}'' used by \cite{cuadra2021my}\cmt{[67]}. This step resulted in 83 unique codes. These codes are then organized based on similarity of their meanings, resulting in 11 aspects of perceptions. For instance, the aspect of personality traits of the agent contains codes such as likeability, funniness, and kindness. Lastly, the 11 aspects are grouped into 4 categories: perception of interaction with agent, perception of agent's ability, perception of sociability with agent, and perception of agent's humanness (\autoref{tbl:perceptions}).

\subsubsection*{Conversation Architecture Elements}
As for the elements of conversation architecture that are relevant to the perception of agents (RQ2), we extracted the speech variation features used in each paper. Some of the papers used multiple features in their CA design, such as the anthropomorphic agent used in Seeger et al's study \cite{seeger2021chatbots}\cmt{[35]}. In these composite situations, we broke the CA design down into its individual features. For example, the design of the anthropomorphic agent \cite{seeger2021chatbots}\cmt{[35]} was divided into features of emotional expressions, is-typing indicator, emoticons, and response delay and captured as separate codes. 58 unique codes were created as part of this process, capturing features like sentiment-adaptive responses \cite{diederich2019emulating}\cmt{[25]}, lexical alignment \cite{spillner2021talk}\cmt{[18]}, and typos \cite{westerman2019believe}\cmt{[9]}. We then organized these codes into elements based on similarity, resulting in 11 elements of conversation architecture. For example, the element of disfluency contains fillers \cite{jeong2019exploring, wester2015artificial}\cmt{[10][14]}, interjections \cite{ceha2022expressive, hu2021enhancing}\cmt{[77][56]}, repetitions \cite{yang2021effect}\cmt{[72]} and typos \cite{westerman2019believe}\cmt{[9]}. These elements are then grouped into 4 categories: dialog strategy, content affectiveness, content style, and speech format (\autoref{tbl:conversation_architecture}).

\subsubsection*{Relationship Between Perceptions of Agents and Conversation Architecture}

\input{figures/fig-heatmap_identified}

To study the effect of conversation architecture on users' perceptions (RQ3), we extracted the connections explored in each paper, using the perception aspects and conversation architecture elements developed in the previous data analysis steps. Each connection's effect was also recorded based on whether an association was found in the study and the nature of that association. Out of our review corpus, 265 connections between perceptions of agents and conversation architecture were explored in literature. To analyze the specifics of conversation architecture that affect the perceptions of CAs, 72 connections that did not result in observed relationships were discarded, resulting in 193 relationships for analysis. For example, the connection between the matching style of a CA and user satisfaction was removed because Hoegen et al. \cite{hoegen2019end}\cmt{[31]} did not find a significant difference between the style matching agent and the non-style matching agent for overall interaction satisfaction. Out of the 193 relationships, 10 were based on comparisons between CAs with multiple speech element variations (e.g. \cite{seeger2021chatbots, volkel2021manipulating}\cmt{[35][68]}). They were not included in the final framework as we could not attribute the perceptions of agents to the individual elements. Overall, 183 relationships between individual conversation architecture elements and perceptions of agents are incorporated into our synthesized framework, visualized as a heatmap to demonstrate their relationships with each other (\autoref{fig:heatmap_identified}).



